The Concurrent Calculi Formalisation Benchmark

### 2024-02-14 short-paper/short-paper.tex
some coinduction

\paragraph{Coinduction.} \todo{explain more what the challenge does.}
Coinduction is fundamental to establish properties of processes that
may never terminate, which is a typical situation. We base our challenge around
bisimulation: a coinductively established property for equating the
observed behaviour of potentially infinite processes.

Common uses for coinduction are to define strong and weak versions of
bisimulation, barbed notions of bisimulation, prove trace equivalence,
etc.

In this challenge we study the notion of strong barbed bisimulation
over a fragment of the $\pi$-calculus.

@@

>>>>

\paragraph{Coinduction.} \todo{explain more what the challenge does.}
Coinduction is fundamental to establish properties of processes that
may never terminate, which is a typical situation.
Common uses for coinduction are to define strong and weak versions of
bisimulation, barbed notions of bisimulation, prove trace equivalence,
etc.

We base our challenge around
bisimulation: a fundamental coinductively established property for equating the
observed behaviour of potentially infinite processes. 
In this challenge, we study the notion of strong barbed bisimulation
(and bisimilarity)
over a fragment of the $\pi$-calculus and,
in particular, we focus on obtaining,
from strong barbed bisimilarity,
a congruence with respect to
parallel composition and substitution.

The introduction of bisimulation
is one of the first steps, when studying the
semantics of process calculi, both
in classical textbooks (e.g., \cite{})
and in almost all existent 
mechanisations \cite{}
(where we see a variety
of different choices).

%Common uses for coinduction are to define strong and weak versions of
%bisimulation, barbed notions of bisimulation, prove trace equivalence,
%etc.

%In this challenge we study the notion of strong barbed bisimulation
%over a fragment of the $\pi$-calculus.

@@

\lore{Need to integrate the following with the above.}
Different process-calculi
mechanisations
implement different techinques;
most of the time these 
are ad-hoc efforts to achieve a specific result.
\lore{cite and substantiate.}
In parallel, although most proof assistants
offer support for coinduction in their standard libraries,
research has mainly focused on the foundations
of the specific system, more than on
applicability.
\lore{cite and substantiate.}
